### 2023-03-02 manuscript.Rmd

  # Process EEG data
  res <- pipeline$group_pipeline(
    vhdr_files = vhdr_files,
    log_files = logs,
    output_dir = output_dir,
    report_dir = report_dir,
    downsample_sfreq = 125.0,
    bad_channels = NULL,
    ica_method = "fastica",
    ica_n_components = 0.99,
    highpass_freq = 0.1,
    lowpass_freq = 30.0,
    triggers = c(221, 222),
    epochs_tmin = -0.5,
    epochs_tmax = 1.5,
    baseline = c(-0.2, 0.0),
    reject_peak_to_peak = 150.0,
    components = list(
      name = list("P1", "N170", "N400"),
      tmin = list(0.1, 0.15, 0.4),
      tmax = list(0.15, 0.2, 0.7),
      roi = list(
        c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
        c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
        c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
      )
    ),
    average_by = list(
      pre_informed =
        "phase == 'Pre-insight' & condition == 'Informed' & rt > 200",
      pre_uninformed =
        "phase == 'Pre-insight' & condition == 'Uninformed' & rt > 200",
      pre_unsuccessful =
        "phase == 'Pre-insight' & condition == 'Unsuccessful' & rt > 200",
      ins_informed =
        "phase == 'Insight' & condition == 'Informed' & rt > 200",
      ins_uninformed =
        "phase == 'Insight' & condition == 'Uninformed' & rt > 200",
      ins_unsuccessful =
        "phase == 'Insight' & condition == 'Unsuccessful' & rt > 200",
      post_informed =
        "phase == 'Post-insight' & condition == 'Informed' & rt > 200",
      post_uninformed =
        "phase == 'Post-insight' & condition == 'Uninformed' & rt > 200",
      post_unsuccessful =
        "phase == 'Post-insight' & condition == 'Unsuccessful' & rt > 200"
    ),
    perform_tfr = TRUE,
    tfr_subtract_evoked = FALSE,
    tfr_freqs = seq(4, 40, by = 1.0),
    tfr_cycles = seq(2, 20, by = 0.5),
    tfr_mode = "percent",
    tfr_baseline = c(-0.45, -0.05),
    perm_contrasts = list(
      c("Pre-insight/Informed", "Pre-insight/Uninformed"),
      c("Insight/Informed", "Insight/Uninformed"),
      c("Post-insight/Informed", "Post-insight/Uninformed"),
      c("Insight/Informed", "Insight/Unsuccessful")
    ),
    tfr_components = list(
      name = list("alpha_beta"),
      tmin = list(0.6),
      tmax = list(1.2),
      fmin = list(8.0),
      fmax = list(20.0),
      roi = list(c("P3", "P4", "Pz", "PO3", "PO4", "POz"))
    ),
    perm_tmin = -0.4,
    perm_tmax = 1.4,
    n_jobs = 4
  )
}

>>>>

  # Process EEG data
  res <- pipeline$group_pipeline(
    vhdr_files = vhdr_files,
    log_files = logs,
    output_dir = output_dir,
    report_dir = report_dir,
    downsample_sfreq = 125.0,
    bad_channels = NULL,
    ica_method = "fastica",
    ica_n_components = 0.99,
    highpass_freq = 0.1,
    lowpass_freq = 30.0,
    triggers = c(221, 222),
    epochs_tmin = -0.5,
    epochs_tmax = 1.5,
    baseline = c(-0.2, 0.0),
    reject_peak_to_peak = 150.0,
    components = list(
      name = list("P1", "N170", "N400"),
      tmin = list(0.1, 0.15, 0.4),
      tmax = list(0.15, 0.2, 0.7),
      roi = list(
        c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
        c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
        c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
      )
    ),
    average_by = list(
      `Pre-insight/Informed` =
        "phase == 'Pre-insight' & condition == 'Informed' & rt > 200",
      `Pre-insight/Uninformed` =
        "phase == 'Pre-insight' & condition == 'Uninformed' & rt > 200",
      `Pre-insight/Unsuccessful` =
        "phase == 'Pre-insight' & condition == 'Unsuccessful' & rt > 200",
      `Insight/Informed` =
        "phase == 'Insight' & condition == 'Informed' & rt > 200",
      `Insight/Uninformed` =
        "phase == 'Insight' & condition == 'Uninformed' & rt > 200",
      `Insight/Unsuccessful` =
        "phase == 'Insight' & condition == 'Unsuccessful' & rt > 200",
      `Post-insight/Informed` =
        "phase == 'Post-insight' & condition == 'Informed' & rt > 200",
      `Post-insight/Uninformed` =
        "phase == 'Post-insight' & condition == 'Uninformed' & rt > 200",
      `Post-insight/Unsuccessful` =
        "phase == 'Post-insight' & condition == 'Unsuccessful' & rt > 200"
    ),
    perform_tfr = TRUE,
    tfr_subtract_evoked = FALSE,
    tfr_freqs = seq(4, 40, by = 1.0),
    tfr_cycles = seq(2, 20, by = 0.5),
    tfr_mode = "percent",
    tfr_baseline = c(-0.45, -0.05),
    perm_contrasts = list(
      c("Pre-insight/Informed", "Pre-insight/Uninformed"),
      c("Pre-insight/Informed", "Pre-insight/Unsuccessful"),
      c("Insight/Informed", "Insight/Uninformed"),
      c("Insight/Informed", "Insight/Unsuccessful"),
      c("Post-insight/Informed", "Post-insight/Uninformed"),
      c("Post-insight/Informed", "Post-insight/Unsuccessful")
    ),
    tfr_components = list(
      name = list("alpha_beta"),
      tmin = list(0.6),
      tmax = list(1.2),
      fmin = list(8.0),
      fmax = list(20.0),
      roi = list(c("P3", "P4", "Pz", "PO3", "PO4", "POz"))
    ),
    perm_tmin = -0.4,
    perm_tmax = 1.4,
    n_jobs = 8
  )
}
